Submission to the Journal of the Royal Statistical Society, Series C (Applied Statistics) 

### 2024-02-19 manuscript_rss/cover_letter.Rmd
country cover letter

* Damien Dupré (corresponding author and main investigator of the study)
  * Dublin City University
  * damien.dupre@dcu.ie
* Edgar Morgenroth
  * Dublin City University
  * edgar.morgenroth@dcu.ie

>>>>

* Damien Dupré (corresponding author and main investigator of the study)
  * affiliation: Business School, Dublin City University
  * city: Dublin
  * country: Ireland
  * email: damien.dupre@dcu.ie

* Edgar Morgenroth
  * affiliation: Business School, Dublin City University
  * city: Dublin
  * country: Ireland
  * email: edgar.morgenroth@dcu.ie
